Spatial modelling of the electoral two-party preferred vote in Australia. A study of federal elections between 2001 and 2016 via the `eechidna` `R` package.

### 2019-03-31 draft-paper.Rmd

# Order electorates in alphabetical order to match spatial matrix
model_df <- small_df %>% 
  arrange(year, DivisionNm) %>% 
  dplyr::select(order(colnames(.))) %>% 
  rename(ManagerAdmin = ManagerAdminClericalSales, 
    OtherLanguage = OtherLanguageHome,
    BornSEEuro = BornSEEurope,
    BornAsia = Born_Asia)
```

>>>>

# Order electorates in alphabetical order to match spatial matrix
model_df <- small_df %>% 
  arrange(year, DivisionNm) %>% 
  dplyr::select(order(colnames(.))) %>% 
  rename(ManagerAdmin = ManagerAdminClericalSales, 
    OtherLanguage = OtherLanguageHome,
    BornSEEuro = BornSEEurope,
    BornAsia = Born_Asia)

```
